---
title: "Risk Analysis of Richtech Robotics (RR)"
subtitle: "R based Quantitative Assessment"
format: html
editor: visual
---

# Risk Analysis of Richtech Robotics (RR)

## Purpose

This report evaluates the return behavior, volatility profile, downside risk, and market sensitivity of Richtech Robotics (RR) using daily price data retrieved from Yahoo Finance.

The objective is to quantitatively access Richtech Robotics. I personally have been looking into this stock keenly through news and the Webull trading app. This is a simple analysis project I am performing so that I can explore RR through a more statistical lens, but to also showcase basic quantitative skills.

### R code Setup

```{r}
library(quantmod)
library(PerformanceAnalytics)
library(tidyverse)
library(xts)
library(zoo)
library(scales)


#Function setup
xts_to_df <- function(x, colname = "value") {
  df <- data.frame(
    Date = as.Date(index(x)),
    value = as.numeric(coredata(x))
  )
  names(df)[2] <- colname
  df
}

getSymbols("RR", src = "yahoo", from = "2025-01-01")
getSymbols("^GSPC", src = "yahoo", from = "2025-01-01")

rr_returns <- dailyReturn(Cl(RR))
sp_returns <- dailyReturn(Cl(GSPC))

```

## Price Trend Analysis

The price chart below shows the historical movement of the RR stock over the selected time horizon (2025, recent).

```{r}
#Price Chart
rr_price <- Ad(RR)
rr_price_df <- xts_to_df(rr_price, "Price")

ggplot(rr_price_df, aes(Date, Price)) +
  geom_line(linewidth = 0.9) +
  scale_y_continuous(labels = dollar_format()) +
  labs(
    title = "Richtech Robotics (RR) — Adjusted Close Price",
    x = NULL, y = "Price (USD)"
  ) +
  theme_minimal(base_size = 13)

#Benchmark S&P 500
sp_price <- Ad(GSPC)
sp_price_df <- xts_to_df(sp_price, "Price")

ggplot(sp_price_df, aes(Date, Price)) +
  geom_line(linewidth = 0.9) +
  labs(
    title = "S&P 500 (^GSPC) — Adjusted Close",
    x = NULL, y = "Index Level"
  ) +
  theme_minimal(base_size = 13)
```

-   RR traded between approximately \$1.50 (March 2025 low) and \$6.80 (October 2025 peak), representing a peak to trough swing of over 350% within the sample period.

-   From January 2025 (\~\$3.00) to February 2026 (\~\$3.00), the net price change is roughly 0%, despite extreme intra-year volatility.

-   The stock experienced multiple 50-100% directional moves within short timeframes, particularly during the late-Q3 to early-Q4 rally.

**Real World Insight -** Large intra-year swings combined with flat net performance indicate speculative trading behavior - high opportunity potential but low price stability for long-term capital preservation.

## Benchmark Comparison - S&P 500

-   The S&P 500 declined from \~6000 to \~5000 in early 2025 (17%), then steadily recovered to \~6900 by early 2026 (\~+38% from trough).

-   Unlike RR, the index exhibited a consistent upward recovery trend post-April 2025.

-   The market's total move (\~+15-20% net) was materially smaller than RR's 300%+ internal swings.

**Real World Insight -** The broad market displayed structured reocvery and stability, highlighting how RR's volatiltiy is firm-specific rather than purely macro-driven.

## Daily Returns

The plot below shows the daily returns volatility graph of RR.

```{r}
#Daily Returns
rr_ret_df <- xts_to_df(rr_returns, "Return")

ggplot(rr_ret_df, aes(Date, Return)) +
  geom_line(linewidth = 0.6) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(
    title = "RR — Daily Returns",
    x = NULL, y = "Daily Return"
  ) +
  theme_minimal(base_size = 13)
```

-   RR experienced single-day returns exceeding +65% and losses approaching -25%.

-   Most daily returns cluster between -5% and 5%, but extreme outliers materially widen dispersion.

-   The magnitude of positive outliers is larger than negative ones, suggesting episodic speculative surges.

**Real World Insight -** Frequent large return spikes increase liquidity and gap risk, dangerous for leveraged or short-term positions.

## Distribution of Returns

```{r}

#Returns Distribution
ggplot(rr_ret_df, aes(Return)) +
  geom_histogram(bins = 40, color = "white") +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(
    title = "RR — Distribution of Daily Returns",
    x = "Daily Return", y = "Count"
  ) +
  theme_minimal(base_size = 13)
```

-   The return distribution is visibly right-skewed, with extreme positive outliers above +70%.

<!-- -->

-    Left tail observations extend to approximately -25%, confirming meaningful downside risk.

<!-- -->

-    The bulk of returns concentrate near 0%, but tail thickness indicates non-normal behavior.

**Real World Insight -** Risk models assuming normal distribution likely underestimate RR’s true tail exposure, particularly during momentum-driven rallies.

## Rolling Volatility

```{r}

#Rolling Volatility
roll_vol_30 <- rollapply(rr_returns, width = 30, FUN = sd, align = "right", fill = NA) * sqrt(252)
roll_vol_df <- xts_to_df(roll_vol_30, "Volatility")

ggplot(roll_vol_df, aes(Date, Volatility)) +
  geom_line(linewidth = 0.9) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(
    title = "RR — 30-Day Rolling Volatility (Annualized)",
    x = NULL, y = "Volatility"
  ) +
  theme_minimal(base_size = 13)
```

-   Rolling volatility peaked above 260% annualized in early 2025.

<!-- -->

-    Volatility stabilized near 70–90% mid-year, then re-accelerated to 180%+ entering early 2026.

<!-- -->

-    Even at its lowest point, volatility remained above 60%, far exceeding typical large-cap levels (\~15–20%).

**Real World Insight -** Sustained volatility above 100% annualized classifies RR as high-risk equity unsuitable for low volatility portfolios.

## Cumulative Returns

```{r}
#Cumulative Returns
both <- merge(rr_returns, sp_returns, join = "inner")
colnames(both) <- c("RR", "Market")
cum <- cumprod(1 + both) - 1
cum_df <- data.frame(Date = as.Date(index(cum)),
                     RR = as.numeric(cum$RR),
                     Market = as.numeric(cum$Market))
cum_long <- tidyr::pivot_longer(cum_df, cols = c("RR","Market"),
                               names_to = "Series", values_to = "CumReturn")
ggplot(cum_long, aes(Date, CumReturn, color = Series)) +
  geom_line(linewidth = 0.9) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(
    title = "Cumulative Returns: RR vs S&P 500",
    x = NULL, y = "Cumulative Return"
  ) +
  theme_minimal(base_size = 13) +
  theme(legend.title = element_blank())
```

-   RR reached a cumulative return peak near +190% in October 2025.

<!-- -->

-    However, it retraced to approximately +20% by early 2026 — a drawdown of roughly 170 percentage points.

<!-- -->

-    Over the same period, the S&P 500 steadily gained approximately 15–20% with significantly lower variance.

**Real World Insight -** RR demonstrates high upside convexity but poor return retention, indicating momentum driven rallies and significant capital erosion.

## Drawdowns

```{r}
#Drawdown Chart
dd <- Drawdowns(rr_returns)  # xts drawdowns (<= 0)
dd_df <- xts_to_df(dd, "Drawdown")

ggplot(dd_df, aes(Date, Drawdown)) +
  geom_area() +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(
    title = "RR — Drawdowns Over Time",
    x = NULL, y = "Drawdown"
  ) +
  theme_minimal(base_size = 13)
```

-   Maximum drawdown reached approximately -65% during early 2025.

<!-- -->

-    Drawdowns frequently remained below -40% for extended periods.

<!-- -->

-    Recovery cycles were volatile and incomplete before new downturns occurred.

**Real World Insight -** A +60% drawdown materially increases behavioral risk, as many investors exit before full recovery which locks in losses.

## 95% Historical VaR

```{r}
#VaR on Returns
ret_vec <- as.numeric(na.omit(rr_returns))
var95 <- quantile(ret_vec, 0.05)  # 5th percentile (loss threshold)

ggplot(rr_ret_df, aes(Return)) +
  geom_histogram(bins = 40, color = "white") +
  geom_vline(xintercept = var95, linewidth = 1, linetype = "dashed") +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(
    title = "RR — Daily Returns with 95% Historical VaR",
    x = "Daily Return", y = "Count",
    caption = paste0("95% Historical VaR ≈ ", scales::percent(var95, accuracy = 0.01))
  ) +
  theme_minimal(base_size = 13)
```

-   The 95% VaR threshold appears near approximately -8% to -10% daily.

<!-- -->

-    This implies that on 5% of trading days, losses exceed roughly 8–10%.

<!-- -->

-    Tail observations extend significantly beyond the VaR cutoff.

**Real World Insight -** A potential 8-10% daily loss places RR among highly volatile small cap equities and increases margin risk exposure.

## Beta Regression (RR vs. Market)

```{r}
#Beta Graph
both_df <- data.frame(
  RR = as.numeric(na.omit(both$RR)),
  Market = as.numeric(na.omit(both$Market))
)

ggplot(both_df, aes(Market, RR)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 1) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(
    title = "RR vs Market — Beta Regression (Daily Returns)",
    x = "Market Return (S&P 500)", y = "RR Return"
  ) +
  theme_minimal(base_size = 13)
```

-   The regression slope visually suggests a beta near **\~2.5–3.0**, indicating amplified sensitivity to market movements.

<!-- -->

-    The dispersion of points around the regression line suggests moderate R² (visible idiosyncratic risk).

<!-- -->

-    Extreme RR moves occur even when market returns are near zero.

**Real World Insight -** RR exhibits both high systematic risk (beta \> 2) and substantial firm specific risk which makes it highly sensitive to both macro shocks and company specific events.

## Conclusion of Discoveries

```{r}
#Summary Metrics
ann_vol <- sd(ret_vec) * sqrt(252)
mean_ret <- mean(ret_vec)
sharpe <- (mean_ret / sd(ret_vec)) * sqrt(252)  # simple Sharpe w/ rf≈0

metrics <- data.frame(
  Metric = c("Mean Daily Return", "Annualized Volatility", "Simple Sharpe (rf≈0)", "95% Hist VaR (Daily)"),
  Value  = c(
    percent(mean_ret, accuracy = 0.01),
    percent(ann_vol, accuracy = 0.01),
    round(sharpe, 2),
    percent(var95, accuracy = 0.01)
  )
)
knitr::kable(metrics, caption = "Summary Risk Metrics for RR")
metrics
```

-   RR exhibits extreme volatility, with annualized rolling volatility exceeding 250% at peak.

<!-- -->

-    Maximum drawdowns of \~65% indicate significant capital erosion risk.

<!-- -->

-    VaR suggests potential 8–10% daily downside in stressed conditions.

<!-- -->

-    Beta above 2 indicates amplified reaction to market movements.

<!-- -->

-    Performance is characterized by explosive rallies followed by deep retracements.

### Overall Assessment of RR:

Richtech Robotics (RR) demonstrates characteristics consistent with a speculative, high-beta small-cap equity featuring substantial tail risk, time-varying volatility, and elevated drawdown exposure. While upside potential is significant, capital stability risk is equally pronounced.

Investors will have to consistently stay up to date with company events and world news, and keep in touch with any event that can negatively effect RR's growth.
